### 2019-09-27 conflog.tex
adds air travel costs

>>>>

\begin{center}
   \begin{tabular}{lccc}
    School & Departure City & O'Hare (ORD) &Willard (CMI) \\
    \hline
    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
    \hline
    Average Lowest Cost for Air Travel&$\$$293&&

    \end{tabular}
